Analyzing MLG distribution

### 2017-10-31 doc/RMD/MLG-distribution.Rmd
add code to export genotype curves

```{r genotype_curves, fig.width = 5, fig.height = 5}
locus_table(dat)
set.seed(2017-06-28)
genotype_curve(dat, sample = 1000, quiet = TRUE)
genotype_curve(dat11, quiet = TRUE)
```

>>>>

```{r genotype_curves, fig.width = 5, fig.height = 5}
locus_table(dat)
set.seed(2017-06-28)
genotype_curve(dat, sample = 1000, quiet = TRUE)
gt16 <- last_plot() + 
  theme_bw(base_size = 16, base_family = "Helvetica") +
  stat_smooth() +
  ggtitle("Haplotype accumulation curve for 16 loci") +
  ylab("Number of multilocus haplotypes")
genotype_curve(dat11, sample = 1000, quiet = TRUE)
gt11 <- last_plot() + 
  theme_bw(base_size = 16, base_family = "Helvetica") +
  stat_smooth() +
  ggtitle("Haplotype accumulation curve for 11 loci") +
  ylab("Number of multilocus haplotypes")
```

```{r saveplots}
if (!interactive()){
  ggsave(gt16,
    filename = "results/figures/publication/genotype-curve16.pdf", 
    width = 88*1.66, 
    height = 88, 
    units = "mm", 
    scale = 1)
  ggsave(gt11,
    filename = "results/figures/publication/genotype-curve11.pdf", 
    width = 88*1.66, 
    height = 88, 
    units = "mm", 
    scale = 1)
}
```
